Concurrent Programming in Harmony

### 2021-12-23 book/paper.tex
Latest

The exercises below have you try the same thing in Python.  As you will
see, the bug is not easily triggered when you run a Python version of
the program.  But in Harmony Murphy's Law applies:
if something can go wrong, it will.  Usually that is not a good thing,
but in Harmony it is.  It allows you to find bugs in your concurrent
programs much more easily than with a conventional programming language.

@@

The following exercises are intended to show you that while it is just
as easy to write concurrent programs in Python, it is much easier to
find concurrency bugs using Harmony.

>>>>

The exercises below have you try the same thing (having threads
concurrently increment an integer variable) in Python.  As you will
see, the bug is not easily triggered when you run a Python version of
the program.  But in Harmony Murphy's Law applies:
if something can go wrong, it will.  Usually that is not a good thing,
but in Harmony it is.  It allows you to find bugs in your concurrent
programs much more easily than with a conventional programming language.

@@

% The following exercises are intended to show you that while it is just
% as easy to write concurrent programs in Python, it is much easier to
% find concurrency bugs using Harmony.
